Second-Generation Web Interface to Correcting ASR output

### 2018-03-31 2018-ftc-vancouver/webapp.tex
row margin for tabularx
rant about ergonomy

% to typeset URLs, URIs, and DOIs
\usepackage{url}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{enumitem}

@@

\subsection{Transcription Apps}

@@

>>>>

% to typeset URLs, URIs, and DOIs
\usepackage{url}
\usepackage{graphicx}
\usepackage{tabularx}
\setlength{\extrarowheight}{6pt}
\usepackage{enumitem}

@@

\subsection{Transcription Apps}
\label{ssec:diff:trans}

@@

\subsection{Ergonomy}

It is clear that the ease of use is crucial in our case where the user is
supposed to perform a requiring, tedious task with repeated steps, especially
since it is our interest more than hers that she performs them. We compared our
setting with that of transcription apps in section~\ref{ssec:diff:trans},
pointing out lessons to learn. Let's now look at some specific points and their
actual (lack of) implementation.

\subsubsection{Keyboard Shortcuts}

One of the most profound measures in ergonomy are keyboard shortcuts. The most
common task is pausing and resuming playback. Both oTranscribe and Transcribe
use the \texttt{esc} key for that, and Transcriber uses the \texttt{tab} key.
We chose \texttt{ctrl+space} combination. We argue that \texttt{esc} is not the
best of options because the distance the fingers have to travel from the
alphanumeric keys causes a noticeable delay. This can lead to missing a pause
between words. The \texttt{tab} key as chosen by Transcriber is a stellar choice
from the ergonomy point of view and there is no reason not to use it in a
dedicated user interface. However, in the browser, where the \texttt{tab} key
has as native use, re-binding it could lead to confusion and irritation. The
space bar is probably the easiest-to-find key in all situations and dedicating
\texttt{ctrl} to all application-specific commands as opposed to single keys
lends a sense of consistency, we believe.

This is speculation though, as we had no resources so far to perform serious
research to support these statements.

The only other keyboard shortcut we support is \texttt{ctrl+enter} for
submitting the correction. We chose this to stay consistent using the
\texttt{ctrl} key and because this shortcut is familiar to users of many instant
messengers, like the Facebook chat or the once popular official ICQ client.
Also, requiring a key combination prevents accidental submission, which is
desirable as we only want double-checked, guaranteed-precise ones. In
comparison, Transcriber uses the base \texttt{enter} key to separate utterances.
oTranscribe and Transcribe allow free formatting with no explicit alignment, so
using the enter key to split utterances by lines is the user's choice.

\subsubsection{Missing Features}

One of the features that Transcribe, the only commercial tool in our reference
list, offers is setting up keyboard shortcuts for common words. We haven't
implemented this because ideally, common words should be covered by the speech
recognition. However, it could be sensible to implement it anyway. The reason is
that a word can be very rare globally and thus poorly recognized by ASR but very
common in a specific passage. This particularly regards named entities.

Another point in our ergonomy to-do list is lifting the need to select a segment
prior to correcting it. If the transcription was simply editable, it could
increase the ease of use rapidly. We would have to automate the selection of
segment to send for forced alignment but we could probably do a better job than
the user in the end.
